Worflow

### 2017-06-06 R/workflow.Rmd
add html

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m9", "m6"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

@@

```{r refit_zinb}
mod <- model.matrix(~ batch[our_cl != "-1"])
fn <- '../data/refit_zinbwave_slingshot.rda'
if (run & !file.exists(fn)){
  zinbList <- lapply(Kvec, function(k){
    zinbFit(core[, our_cl != "-1"], X = mod, K = k, ncores = NCORES)
  })
  save(zinbList, file = fn)
}else{
  load(fn)
}
```

@@

  lineages <- get_lineages(X, clus.labels = our_cl, start.clus = "m1",
                           end.clus = c("m9", "m6"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

>>>>

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m8", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

@@

```{r refit_zinb}
mod <- model.matrix(~ batch[our_cl != "-1"])
fn <- '../data/refit_zinbwave_slingshot.rda'
if (runZinb & !file.exists(fn)){
  zinbList <- lapply(Kvec, function(k){
    zinbFit(core[, our_cl != "-1"], X = mod, K = k, ncores = NCORES)
  })
  save(zinbList, file = fn)
}else{
  load(fn)
}
```

@@

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m8", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)
